Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Tried to work on MNIST another layout

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist)

tr_from_to_df_mnist <- inner_join(
  tr_from_to_df_mnist, distance_df_small_edges_mnist, 
  by = c("from", "to"))

@@

df_model_data_mnist_n <- bind_rows(data_mnist_cluster, df_b_mnist)

>>>>

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) #benchmark_mnist

tr_from_to_df_mnist <- right_join(
  tr_from_to_df_mnist, distance_df_small_edges_mnist, 
  by = c("from", "to"))

@@

df_model_data_mnist_n <- bind_rows(df_b_mnist, data_mnist_cluster)
